The Dynamics of Normalization Reweighting (target journal: Neuron)

### 2022-05-24 manuscript.Rmd
Preprocessing for main EEG experiment

@@

hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)
legaltriggers <- hdata$Trigger[!is.na(hdata$Trigger)]
subcounter <- 0

for (s in 1:101) {
  if (s != 75) {
    subcounter <- subcounter + 1  
  if (!file.exists(paste0('temp/VilidaiteProcessed/V',subcounter,'processed.RData'))){
  print(s)

@@

     save(file = paste0('temp/VilidaiteProcessed/V',subcounter,'processed.RData'), list = c('meanwaveforms','electrodes'))

@@

subjcounter <- 0
for (datahalf in 1:length(EEGID)){
  EEGtoken <- componentlist[EEGID[datahalf],2]
  EEGfiles <- osf_ls_files(EEGtoken,n_max=300)
  for (f in 1:nrow(EEGfiles)){
    subjcounter <- subcounter + 1

    # first check if we have this participant's data
    if (!file.exists(paste0('temp/EEGprocessed/S',subjcounter,'data.RData'))){
      # if we haven't processed the data, check if we need to download the raw data
      if (!dir.exists(paste0('temp/raw/S',subjcounter))){
        if (!file.exists(paste0('temp/raw/S',subjcounter,'.zip'))){
          osf_download(EEGfiles[f,], path='temp/raw/',progress=TRUE)
        }
          unzip(paste0('temp/raw/S',subjcounter,'.zip'),exdir='temp/raw/')
          file.remove(paste0('temp/raw/S',subjcounter,'.zip'))
      }
    # if necessary, process the data for this participant

@@

     triggertimes <- (1:64) * 0
    counter <- 0
    for (n in 1:nrow(EEGdata)) {
      if (EEGdata$Trigger[n] %in% legaltriggers) {
        counter <- counter + 1
        triggertimes[counter] <- n
      }
    }

     for (tr in 1:counter) {
      cond <- which(legaltriggers == EEGdata$Trigger[triggertimes[tr]])
      cond <- ceiling(cond/2)
      condcounter[cond] <- condcounter[cond] + 1

@@

          spec5 <- NULL
          spec7 <- NULL
          for (t in 1:condcounter[cond]){
            spec <- fft(temp[t,1501:7500])
            spec5[t] <- spec[6*5+1]
            spec7[t] <- spec[7*5+1]
          }
        spec5[which(is.na(spec5))] <- 0
        spec7[which(is.na(spec7))] <- 0
      if (sum(abs(spec5))>0){  
      tempxy <- data.frame(Re(spec5),Im(spec5))
      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
      tempxy <- data.frame(Re(spec7),Im(spec7))
      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
      i <- which(D5<3 & D7<3)
      trialsincluded[cond,ch] <- length(i)
      subjwaves[cond,,ch] <- colMeans(temp[i,])
      }   
        }
      }

@@

d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)

groupmeans <- array(0,dim=c(length(d),4,4,10))
groupspec <- array(0,dim=c(length(d),4,64,121))
groupspecplot <- array(0,dim=c(length(d),4,121))
groupwaveforms <- array(0,dim=c(length(d),4,8000))
EEGtimecourse5Hz <- array(0,dim=c(length(d),4,7000))
EEGtimecourse7Hz <- array(0,dim=c(length(d),4,7000))

for (s in 1:length(d)){
  load(d[s])

  # remove any NaN values
  chanspec[which(is.na(chanspec))] <- 0
  allspec[which(is.na(allspec))] <- 0
  allsamples[which(is.na(allsamples))] <- 0

  ch <- match(targetelectrodes, electrodes) - 2

  meanchanspec <- (apply(chanspec,2:4,mean))
  spectoplot <- (apply(chanspec[,,ch,],c(2,4),mean))

  meanspec <- (apply(allspec,2:4,mean))
  for (f in 1:4){
    for (cond in 1:4){
      for (t in 1:10){
        temp <- allspec[,f,cond,t]
        tempxy <- data.frame(Re(temp),Im(temp))
        D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
        i <- which(D<3)
        meanspec[f,cond,t] <- (mean(temp[i]))
      }
    }
  }
  meanwaves <- apply(allsamples,2:3,mean)

  for (cond in 1:4){
   fspec1 <- NULL
fspec2 <- NULL
for (t in 1:(8000-binwidth)){
  spec <- fft(meanwaves[cond,t:(t+binwidth-1)])/binwidth
  fspec1[t] <- spec[tindex]
  fspec2[t] <- spec[mindex]
}
    EEGtimecourse5Hz[s,cond,] <- fspec1
    EEGtimecourse7Hz[s,cond,] <- fspec2 
  }

  meanwaves <- meanwaves - mean(meanwaves)
  meanwaves <- meanwaves / max(abs(meanwaves))
  groupmeans[s,,,] <- meanspec
  groupspec[s,,,] <- meanchanspec
  groupspecplot[s,,] <- spectoplot
  groupwaveforms[s,,] <- meanwaves

save(file='temp/EEGsummary.RData',list=c('groupmeans','groupspecplot','groupwaveforms','groupspec','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))

if (runcode==1){
load('temp/EEGsummary.RData')

meanspec <- abs(apply(groupmeans,c(2,3,4),mean))
spectoplot <- abs(apply(groupspecplot,c(2,3),mean))
meanwaves <- apply(groupwaveforms,c(2,3),mean)
meanchanspec <- abs(apply(groupspec,c(2,3,4),mean))

EEGmeantime5Hz <- matrix(0,nrow=4,ncol=7000) 
EEGmeantime7Hz <- matrix(0,nrow=4,ncol=7000) 
for (cond in 1:4){
EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean)
EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean)
}

pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 10)

times <- ((1:7000)-500)/1000

plotlims <- c(-1,8,0,1)
ticklocsx <- -1:8    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
ticklabelsx <- -1:8        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(times,EEGmeantime5Hz[1,],lwd=2,col='red')
lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
lines(times,EEGmeantime5Hz[3,],lwd=2,col='blue')
lines(times,EEGmeantime5Hz[4,],lwd=2,col='orange')

spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
lines(spl5a$x,spl5a$y,col='red',lwd=2)
spl5b <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
lines(spl5b$x,spl5b$y,col='green',lwd=2)
spl5c <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
lines(spl5c$x,spl5c$y,col='blue',lwd=2)
spl5d <- smooth.spline(times,EEGmeantime5Hz[4,],df=20)
lines(spl5d$x,spl5d$y,col='orange',lwd=2)

plotlims <- c(-1,8,0,2) 
ticklocsx <- -1:8    # locations of tick marks on x axis
ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
ticklabelsx <- -1:8        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[3,],col='blue',lwd=2)
lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[4,],col='orange',lwd=2)

lines(spl5a$x,spl5a$y/spl5c$y,col='blue',lwd=2)
lines(spl5a$x,spl5a$y/spl5d$y,col='orange',lwd=2)

plotlims <- c(-1,8,0,1) 
ticklocsx <- -1:8    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(times,EEGmeantime7Hz[1,],lwd=2,col='red')
lines(times,EEGmeantime7Hz[2,],lwd=2,col='green')
lines(times,EEGmeantime7Hz[3,],lwd=2,col='blue')
lines(times,EEGmeantime7Hz[4,],lwd=2,col='orange')

spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
lines(spl7a$x,spl7a$y,col='red',lwd=2)
spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
lines(spl7b$x,spl7b$y,col='green',lwd=2)
spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
lines(spl7c$x,spl7c$y,col='blue',lwd=2)
spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
lines(spl7d$x,spl7d$y,col='orange',lwd=2)

plotlims <- c(-1,8,0,2) 
ticklocsx <- -1:8    # locations of tick marks on x axis
ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
ticklabelsx <- -1:8        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[3,],col='blue',lwd=2)
lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[4,],col='orange',lwd=2)

dev.off()

>>>>

osf_auth(token = '3dEYuhZNmwWbG3xuhRIiVRo0T2oniOkEP3Ip8i1LPG4PNjeTRln54eGNAG7oyTT9xozWwJ')

@@

hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)
legaltriggers <- hdata$Trigger[!is.na(hdata$Trigger)]
subjcounter <- 0

for (s in 1:101) {
  if (s != 75) {
    subjcounter <- subjcounter + 1  
  if (!file.exists(paste0('temp/VilidaiteProcessed/V',subjcounter,'processed.RData'))){
  print(s)

@@

     save(file = paste0('temp/VilidaiteProcessed/V',subjcounter,'processed.RData'), list = c('meanwaveforms','electrodes'))

@@

subjcounter <- 0
for (datahalf in 1:length(EEGID)){
  EEGtoken <- componentlist[EEGID[datahalf],2]
  EEGfiles <- osf_ls_files(EEGtoken,n_max=300)
  for (f in 1:nrow(EEGfiles)){
    subjcounter <- subjcounter + 1
    print(subjcounter)
    # first check if we have this participant's data
    if (!file.exists(paste0('temp/EEGprocessed/S',subjcounter,'data.RData'))){
      # if we haven't processed the data, check if we need to download the raw data
      if (!dir.exists(paste0('temp/raw/S',subjcounter))){
        if (!file.exists(paste0('temp/raw/S',subjcounter,'.zip'))){
          osf_download(EEGfiles[f,], path='temp/raw/',progress=TRUE)
        }
          unzip(paste0('temp/raw/S',subjcounter,'.zip'),exdir='temp/raw/')
          file.remove(paste0('temp/raw/S',subjcounter,'.zip'))
      }
    # if necessary, process the data for this participant

@@

    triggertimes <- NULL
    counter <- 0
    for (n in 1:nrow(EEGdata)) {
      if (EEGdata$Trigger[n] %in% legaltriggers) {
        counter <- counter + 1
        triggertimes[counter] <- n
      }
    }

    # remove the first trial if there is not sufficient pre-trial baseline time
    if (triggertimes[1]<1500){triggertimes <- triggertimes[2:counter]}

     for (tr in 1:length(triggertimes)) {
      cond <- which(legaltriggers == EEGdata$Trigger[triggertimes[tr]])
      cond <- ceiling(cond/2)
      condcounter[cond] <- condcounter[cond] + 1

@@

          spec5 <- NULL
          spec7 <- NULL
          for (t in 1:condcounter[cond]){
            spec <- fft(temp[t,1501:7500])
            spec5[t] <- spec[targetF*duration+1]
            spec7[t] <- spec[maskF*duration+1]
          }
        spec5[which(is.na(spec5))] <- 0
        spec7[which(is.na(spec7))] <- 0
      if (length(which(abs(spec5)>0))>2){  
      tempxy <- data.frame(Re(spec5),Im(spec5))
      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
      tempxy <- data.frame(Re(spec7),Im(spec7))
      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
      i <- which(D5<3 & D7<3)
      trialsincluded[cond,ch] <- length(i)
      subjwaves[cond,,ch] <- colMeans(temp[i,])
      }   
        }
      }

@@

# d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
# groupmeans <- array(0,dim=c(length(d),4,4,10))
# groupspec <- array(0,dim=c(length(d),4,64,121))
# groupspecplot <- array(0,dim=c(length(d),4,121))
# groupwaveforms <- array(0,dim=c(length(d),4,8000))
# EEGtimecourse5Hz <- array(0,dim=c(length(d),4,7000))
# EEGtimecourse7Hz <- array(0,dim=c(length(d),4,7000))
#   load(d[s])
#   # remove any NaN values
#   chanspec[which(is.na(chanspec))] <- 0
#   allspec[which(is.na(allspec))] <- 0
#   allsamples[which(is.na(allsamples))] <- 0
#   ch <- match(targetelectrodes, electrodes) - 2
#   meanchanspec <- (apply(chanspec,2:4,mean))
#   spectoplot <- (apply(chanspec[,,ch,],c(2,4),mean))
#   meanspec <- (apply(allspec,2:4,mean))
#   for (f in 1:4){
#     for (cond in 1:4){
#       for (t in 1:10){
#         temp <- allspec[,f,cond,t]
#         tempxy <- data.frame(Re(temp),Im(temp))
#         i <- which(D<3)
#         meanspec[f,cond,t] <- (mean(temp[i]))
#   meanwaves <- apply(allsamples,2:3,mean)
#   for (cond in 1:4){
#    fspec1 <- NULL
# fspec2 <- NULL
# for (t in 1:(8000-binwidth)){
#   spec <- fft(meanwaves[cond,t:(t+binwidth-1)])/binwidth
#   fspec1[t] <- spec[tindex]
#   fspec2[t] <- spec[mindex]
#     EEGtimecourse5Hz[s,cond,] <- fspec1
#     EEGtimecourse7Hz[s,cond,] <- fspec2 
#   meanwaves <- meanwaves - mean(meanwaves)
#   meanwaves <- meanwaves / max(abs(meanwaves))
#   groupmeans[s,,,] <- meanspec
#   groupspec[s,,,] <- meanchanspec
#   groupspecplot[s,,] <- spectoplot
#   groupwaveforms[s,,] <- meanwaves
# save(file='temp/EEGsummary.RData',list=c('groupmeans','groupspecplot','groupwaveforms','groupspec','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))
# if (runcode==1){
# load('temp/EEGsummary.RData')
# meanspec <- abs(apply(groupmeans,c(2,3,4),mean))
# spectoplot <- abs(apply(groupspecplot,c(2,3),mean))
# meanwaves <- apply(groupwaveforms,c(2,3),mean)
# meanchanspec <- abs(apply(groupspec,c(2,3,4),mean))
# EEGmeantime5Hz <- matrix(0,nrow=4,ncol=7000) 
# EEGmeantime7Hz <- matrix(0,nrow=4,ncol=7000) 
# for (cond in 1:4){
# EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean)
# EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean)
# pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 10)
# par(mfrow=c(2,2))
# times <- ((1:7000)-500)/1000
# plotlims <- c(-1,8,0,1)
# ticklocsx <- -1:8    # locations of tick marks on x axis
# ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
# ticklabelsx <- -1:8        # set labels for x ticks
# ticklabelsy <- ticklocsy    # set labels for y ticks
# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
# title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
# lines(times,EEGmeantime5Hz[1,],lwd=2,col='red')
# lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
# lines(times,EEGmeantime5Hz[3,],lwd=2,col='blue')
# lines(times,EEGmeantime5Hz[4,],lwd=2,col='orange')
# spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
# lines(spl5a$x,spl5a$y,col='red',lwd=2)
# spl5b <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
# lines(spl5b$x,spl5b$y,col='green',lwd=2)
# spl5c <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
# lines(spl5c$x,spl5c$y,col='blue',lwd=2)
# spl5d <- smooth.spline(times,EEGmeantime5Hz[4,],df=20)
# lines(spl5d$x,spl5d$y,col='orange',lwd=2)
# plotlims <- c(-1,8,0,2) 
# ticklocsx <- -1:8    # locations of tick marks on x axis
# ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
# ticklabelsx <- -1:8        # set labels for x ticks
# ticklabelsy <- ticklocsy    # set labels for y ticks
# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
# title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
# lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[3,],col='blue',lwd=2)
# lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[4,],col='orange',lwd=2)
# lines(spl5a$x,spl5a$y/spl5c$y,col='blue',lwd=2)
# lines(spl5a$x,spl5a$y/spl5d$y,col='orange',lwd=2)
# plotlims <- c(-1,8,0,1) 
# ticklocsx <- -1:8    # locations of tick marks on x axis
# ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
# title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
# lines(times,EEGmeantime7Hz[1,],lwd=2,col='red')
# lines(times,EEGmeantime7Hz[2,],lwd=2,col='green')
# lines(times,EEGmeantime7Hz[3,],lwd=2,col='blue')
# lines(times,EEGmeantime7Hz[4,],lwd=2,col='orange')
# spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
# lines(spl7a$x,spl7a$y,col='red',lwd=2)
# spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
# lines(spl7b$x,spl7b$y,col='green',lwd=2)
# spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
# lines(spl7c$x,spl7c$y,col='blue',lwd=2)
# spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
# lines(spl7d$x,spl7d$y,col='orange',lwd=2)
# plotlims <- c(-1,8,0,2) 
# ticklocsx <- -1:8    # locations of tick marks on x axis
# ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
# ticklabelsx <- -1:8        # set labels for x ticks
# ticklabelsy <- ticklocsy    # set labels for y ticks
# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
# title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
# lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[3,],col='blue',lwd=2)
# lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[4,],col='orange',lwd=2)
# lines(spl7b$x,spl7b$y/spl7c$y,col='blue',lwd=2)
# lines(spl7b$x,spl7b$y/spl7d$y,col='orange',lwd=2)
# dev.off()
